A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
Comment on RKBexplorer
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1065 43ef1190-90fd-4dd7-a769-d0121f02b80e

We also note that prohibition of SPARQL results caching is rare.
Amongst the servers that expose caching headers it is common
that the result may be cached for some minutes, and closer inspection
of the dataset reveals that many of these are due to that
RBKExplorer\footnote{\url{http://www.rkbexplorer.com/}} sets an
freshness lifetime of 300~s for many endpoints.

>>>>

We also note that prohibition of SPARQL results caching is rare.
Amongst the servers that expose caching headers it is common
that the result may be cached for some minutes, and closer inspection
of the dataset reveals that many of these are due to that
RBKExplorer\footnote{\url{http://www.rkbexplorer.com/about/}} sets an
freshness lifetime of 300~s for many endpoints.
